Semantic browsing of sound databases \\ without keywords

### 2016-02-14 lafaySsf2016.tex
submission v1

\title{Semantic browsing of sound databases \\ without keywords}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

As a reference, an Acoustic Display (AD) provides a spatial representation based on acoustic descriptors. Each sound is described by time-averaged Mel-Frequency Cepstrum Coefficients (MFCCs) computed with standard parameter settings (13 lowest quefrency coefficients are kept out of 40). The Euclidean distance between time averaged features is then computed for each sound pair. A non metric multidimensional scaling with Kruskal's normalized stress is then employed to project the data into two dimensions according to this distance, see Figure \ref{figXP3}.

@@

More precisely, with the FSD display, users can directly visualize the whole hierarchy, down to the leaf classes, while with the PSD display, users only have access, at first, to the intermediate semantic levels of the hierarchy. Upon first using PSD, they observe circles representing the top classes of the semantic hierarchical structure of the dataset. When users click on a circle, they hear the sound prototype of the class and the subclasses are progressively revealed, represented by white circles contained in the circle that has just been clicked. The same action repeats itself until the user reaches the leaf classes of the hierarchy. The leaf classes are represented with small gray circles, indicating that there is no subclass to uncover. Thus the PSD has a constrained exploration system. When a user clicks on a circle, sub-circles are  automatically revealed to him in a gradual way. Each time a sub-circle is automatically revealed, its sound prototype is played. Users may stop the discovery process by clicking on an other circle. In this display, the leaf classes are distributed  in the same manner as FSD. Thus, the spatial configuration of the unfolded version of PSD, which may be obtained after discovering all the classes and subclasses, is equivalent to the one of FSD, as shown on Figures~\ref{figXP2}, \ref{figXP1} and \ref{figSSF}.

>>>>

\title{Semantic browsing of sound databases \\ without keywords}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%strain
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

As a reference, an Acoustic Display (AD) provides a spatial representation based on acoustic descriptors. Each sound is described by time-averaged Mel-Frequency Cepstrum Coefficients (MFCCs) computed with standard parameter settings (13 lowest quefrency coefficients are kept out of 40). The Euclidean distance between time averaged features is then computed for each sound pair. A non metric multidimensional scaling with Kruskal's normalized stress \cite{kruskal1964multidimensional} is then employed to project the data into two dimensions according to this distance, see Figure \ref{figXP3}.

@@

More precisely, with the FSD display, users can directly visualize the whole hierarchy, down to the leaf classes, while with the PSD display, users only have access, at first, to the intermediate semantic levels of the hierarchy. Upon first using PSD, they observe circles representing the top classes of the semantic hierarchical structure of the dataset. When users click on a circle, they hear the sound prototype of the class and the subclasses are progressively revealed, represented by white circles contained in the circle that has just been clicked. The same action repeats itself until the user reaches the leaf classes of the hierarchy. The leaf classes are represented with small gray circles, indicating that there is no subclass to uncover. Thus the PSD has a constrained exploration system. Each time a sub-circle is automatically revealed, its sound prototype is played. Users may stop the discovery process by clicking on an other circle. In this display, the leaf classes are distributed  in the same manner as FSD. Thus, the spatial configuration of the unfolded version of PSD, which may be obtained after discovering all the classes and subclasses, is equivalent to the one of FSD, as shown on Figures~\ref{figXP2}, \ref{figXP1} and \ref{figSSF}.
